---
title: "How to use GoogleGeoAPI to retrieve adress information"
author: "Torrin Danner, Joshua Hudson, Sascha Schmalz, and Nikolajs Prihodko"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## GoogleGeoAPI package

This package is intendeed to be used for geocoding. Geocoding is converting addresses from the usual human-readable format to numerical geographic coordinates. For example, "Linköpings Universitet, 58183 Linköping" is converted to "58.40208 15.57901", which are lattitude and longitude of the specified address.

## Installation
To install the package [devtools](https://cran.r-project.org/web/packages/devtools/index.html) should be present on your machine. If you are using [RStudio](https://www.rstudio.com/), you can just run the following command
```{r, eval = FALSE}
install.packages("devtools")
```
If you are using plain R or another development environment, please refere to the package documenation for information on how to install it.

After the installation of `deevtools`, we can simply run the following command in the RStudio console
```{r, eval = FALSE}
devtools::install_github(repo = "https://github.com/Rchieve/GoogleGeoAPI", 
                         build_vignette = TRUE)
```

## Workflow

The workflow can be divided into a few steps

1. Load the package.
2. Specify an adress.
3. Call Google Geo API.
4. Convert the output to geographic coordinates.

### Load the package

First, we want to load the packaged to have access to all the functions in it.
```{r}
library(GoogleGeoAPI)
```

### Specify address

Second, we want to create an `adrs` object from the text format. For example, let us create the object for the Linköpings Universitet. Address should be specified as a string "in the format used by the national postal service of the country concerned". Moreover, we might want to avoid additional address elements. If something does not work, we should to refer to the Goole [FAQ](https://developers.google.com/maps/faq#geocoder_queryformat).

```{r}
liu <- adrs("Linköpings Universitet, 58183 Linköping")
```

To check whether we have passed the correct address, we might want print the object:
```{r}
print(liu)
```

### Geocode

Third, we want to geocode this adress, i.e. that we want to convert it to geographical coordinates.
```{r}

```

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
