---
title: "How to use GoogleGeoAPI to retrieve adress information"
author: "Torrin Danner, Joshua Hudson, Sascha Schmalz, and Nikolajs Prihodko"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## GoogleGeoAPI package

This package is intendeed to be used for geocoding and reverse geocoding. Geocoding is converting addresses from the usual human-readable format to numerical geographic coordinates. For example, "Linköpings Universitet, 58183 Linköping" is converted to "58.40208 15.57901", which are latitude and longitude of the specified address. The reverse geocoding is the reverse process.

## How to install and load

### Install 

To install the package [devtools](https://cran.r-project.org/web/packages/devtools/index.html) should be present on your machine. If you are using [RStudio](https://www.rstudio.com/), you can just run the following command
```{r, eval = FALSE}
install.packages("devtools")
```
If you are using plain R or another development environment, please refer to the package documentation for information on how to install it.

After the installation of `deevtools`, we can simply run the following command in the RStudio console
```{r, eval = FALSE}
devtools::install_github(repo = "https://github.com/Rchieve/GoogleGeoAPI", 
                         build_vignette = TRUE)
```

### Load

After the installation is successful, we want to load the package using

```{r}
library(GoogleGeoAPI)
```

or access function directly, using `GoogleGeoAPI::<function_name>`.


## Workflow

### Geocode

First, we want to create an `adrs` object from the text format. For example, let us create the object for the Linköpings Universitet. Address should be specified as a string "in the format used by the national postal service of the country concerned". Moreover, we might want to avoid additional address elements. If something does not work, we should to refer to the Google [FAQ](https://developers.google.com/maps/faq#geocoder_queryformat).

```{r}
liuAdrs <- adrs("Linköpings Universitet, 58183 Linköping")
```

To check whether we have passed the correct address, we might want print the object:
```{r}
print(liuAdrs)
```

Second, we want to geocode this address, i.e. that we want to convert it to geographical coordinates. This is achieved via the `geocode` function
```{r}
liuGeocoded <- geocode(liuAdrs)
```

This returns a `coord` object.

To print the coordinates type
```{r}
print(liuGeocoded)
```

Or use implicit printing, by running the name of the geocoded object in an R console./
```{r, eval = FALSE}
liuGeocoded
```

To access the latitude or longitude call the fields of the `coord` object:
```{r}
liuGeocoded$lat
liuGeocoded$lon
```

### Reverse geocode

We can also use reverse geocoding, i.e. obtain an address of the coordinates.

First we create a `coord` object. Coordinates should be in decimal format.
```{r}
liuCoord <- coord(58.40208, 15.57901)
```

Then we reverse geocode, i.e. obtain a human-readable address from geographic coordinates, using the `geocode` function
```{r}
liuRGeocoded <- geocode(liuCoord)
```

This returns an `adrs` object. We can either print it
```{r}
print(liuRGeocoded)
```

Or access the address field
```{r}
liuRGeocoded$address
```

As we can see, the `geocode(geocode(adrs(<some_address>)))` might not be equal to `<some_address>`. This happens, because reverse geocoding might return a more precise address than was used for geocoding. In the example above it return the address of a particular building on the Linköpings Universitet campus.
